### 2021-07-13 chapters/7_discussion.tex
fixed our tool to the tool

\section{Application}
The application of our research is limited to all software projects written in the language Java and the limitations of our mutation testing tool PIT\cite{pit}.
We can repeat our experiment for every java project that can be run by PIT.
This scope is significantly larger than most of the research done in the domain of mutation clustering(Chapter \ref{ch:related_work}).
The extraction of mutants is build within the PIT plugin system which is a plug and play system.
Applying our research can be done in three steps.
The first step is to run PIT with the plugin to gather the characteristics.
This plugin makes sure PIT exits without executing mutants after gathering the characteristics.
The second step is to run the script for either the machine learning model or the hierarchical clustering.
The last step is to run PIT again with the plugin to filter the mutants based on the results of the clustering.
It is possible to build all these steps into a DevOps pipeline to automate the process. 
The plugins and scripts needed for these steps are available on Github\cite{rbasarat-repo}.

>>>>

\section{Application}
The application of our research is limited to all software projects written in the language Java and the limitations of the selected mutation testing tool PIT\cite{pit}.
We can repeat our experiment for every java project that can be run by PIT.
This scope is significantly larger than most of the research done in the domain of mutation clustering(Chapter \ref{ch:related_work}).
The extraction of mutants is build within the PIT plugin system which is a plug and play system.
Applying our research can be done in three steps.
The first step is to run PIT with the plugin to gather the characteristics.
This plugin makes sure PIT exits without executing mutants after gathering the characteristics.
The second step is to run the script for either the machine learning model or the hierarchical clustering.
The last step is to run PIT again with the plugin to filter the mutants based on the results of the clustering.
It is possible to build all these steps into a DevOps pipeline to automate the process. 
The plugins and scripts needed for these steps are available on Github\cite{rbasarat-repo}.
